\documentclass[10pt,a4paper,BCOR12mm, headexclude, footexclude,
  twoside, openright]{scrartcl}
\usepackage[scaled]{helvet}
\usepackage[british]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{ifthen}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{sfmath}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{sectsty}
\usepackage{url} %url in footnote
\usepackage{color}
\usepackage{tikz}
\usepackage{graphicx}

%% Listings
\usepackage{listings}
\usepackage{xcolor}

\graphicspath{ {images/} }

%\KOMAoptions{optionenliste}
%\KOMAoptions{Option}{Werteliste}


\addtokomafont{caption}{\small}
%\setkomafont{descriptionlabel}{\normalfont
%   \bfseries}
\setkomafont{captionlabel}{\normalfont
    \bfseries}
\let\oldtabular\tabular
\renewcommand{\tabular}{\sffamily\oldtabular}
\KOMAoptions{abstract=true}
%\setkomafont{footnote}{\sffamily}
%\KOMAoptions{twoside=true}
%\KOMAoptions{headsepline=true}
%\KOMAoptions{footsepline=true}
\renewcommand\familydefault{\sfdefault}
\renewcommand{\arraystretch}{1.1}
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}}
\setlength{\textheight}{230mm}
\allsectionsfont{\centering \normalfont\scshape}
\let\tmp\oddsidemargin
\let\oddsidemargin\evensidemargin
\let\evensidemargin\tmp
\reversemarginpar

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt}

%%%% Listings
% C#
%\setmonofont{Consolas} %to be used with XeLaTeX or LuaLaTeX
\definecolor{bluekeywords}{rgb}{0,0,1}
\definecolor{greencomments}{rgb}{0,0.5,0}
\definecolor{redstrings}{rgb}{0.64,0.08,0.08}
\definecolor{xmlcomments}{rgb}{0.5,0.5,0.5}
\definecolor{types}{rgb}{0.17,0.57,0.68}

\usepackage{listings}
\lstset{language=[Sharp]C,
captionpos=b,
%numbers=left, %Nummerierung
%numberstyle=\tiny, % kleine Zeilennummern
frame=lines, % Oberhalb und unterhalb des Listings ist eine Linie
showspaces=false,
showtabs=false,
breaklines=true,
showstringspaces=false,
breakatwhitespace=true,
escapeinside={(*@}{@*)},
commentstyle=\color{greencomments},
morekeywords={partial, var, value, get, set},
keywordstyle=\color{bluekeywords},
stringstyle=\color{redstrings},
basicstyle=\ttfamily\small,
}

\begin{document}
%\sffamily
\fancypagestyle{plain}
{%
  \renewcommand{\headrulewidth}{0pt}%
  \renewcommand{\footrulewidth}{0.5pt}
  \fancyhf{}%
  \fancyfoot[R]{\emph{\footnotesize Page \thepage\ of \pageref{LastPage}}}%
  \fancyfoot[C]{\emph{\footnotesize Christophe De Troyer and Maarten Vandercammen}}%
}

\thispagestyle{plain}

\titlehead
{
    Vrije Universiteit Brussel\\%
    Pleinlaan 2\\%
    Software Languages Lab - Dept. Of Computer Science\hfill
    Master Studies%
}
\subject{\vspace{-1ex} \horrule{2pt}\\[0.15cm]
  {\textsc{\texttt{Capita Selecta: Software Engineering}}}}
\title{Project Software Engineering\\[0.5cm]}
\subtitle{\textsc{\texttt{Deliverable 1}}\\\horrule{2pt}\\[0.5cm]}
\author{
  \bfseries{Christophe De Troyer}\vspace{-2ex}
  \and
  \bfseries{Maarten Vandercammen}\vspace{-2ex} 
}
\date{\begin{tabular}{cc}
  \textsc{Date:}& \textsc{\emph{\today}}\\
  \textsc{Due :}& \textsc{\emph{9th March 2015}}\vspace{3ex}
\end{tabular}}
\maketitle

%\begin{abstract}
%\end{abstract}
\newpage

\tableofcontents

\newpage

%-------------------------------
\fancypagestyle{plain}
{%
  \renewcommand{\headrulewidth}{0.5pt}%
  \renewcommand{\footrulewidth}{0.5pt}
  \fancyhf{}%
  \fancyhead[R]{\emph{\footnotesize \today}}
  \fancyfoot[R]{\emph{\footnotesize Page \thepage\ of \pageref{LastPage}}}%
  \fancyfoot[C]{\hspace*{-1.5cm} \emph{\footnotesize Christophe De Troyer} \hspace{2.7cm} \emph{\footnotesize Maarten Vandercammen} \\ \hspace*{-2cm} \emph{\footnotesize 106490} \hspace{4.5cm} \emph{\footnotesize 98341}}%
}

\pagestyle{plain}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Project Description
\section{Project Description}
The project we (i.e., Christophe De Troyer and Maarten Vandercammen) are using
for this course is named ``CodeBox''. CodeBox is a project built by Christophe
De Troyer during his studies for a Bsc at Ghent College. It is a web
application built using the Microsoft .NET web stack. It uses MVC 3 as architectural
pattern, Entity Framework for the persistence layer and C\# as the language of
choice. The views are constructed using the then-new markup language Razor.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Functionality
\subsection{Functionality}
\paragraph{Snippets}
CodeBox is basically a clone of pastebin.net (or any other text-sharing
website). The main idea of the website is to allow users to upload snippets of
code using the webinterface and share them with other users. If wanted, the
snippets can be kept private as well. Snippets can be given a title and
description for future reference. Existing snippets can also be edited by their creator.

\paragraph{Groups}
To differentiate a bit from pastebin.net the notion of groups was
introduced. This allows a user to create a group and add other members of
CodeBox to that group. This gives one the option to share snippets not only with everyone (i.e., public) or nobody (i.e., private) but with all members from the selected groups as well. 
Users are however not allowed to edit snippets created by a different user in that group.\\ Finally, groups have some sort of profile. Administrators of a group can modify the name, description and profile picure of a group. They can also invite new members to a group by adding their e-mail address to the list. This e-mail has to be a valid and existing user for the system to work.

\paragraph{Users}
The last small feature of CodeBox is that users can edit their profile. It is
possible to provide a full name (first and surname). The user can change his/her
password and upload a profile picture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Testability
\section{Testability}
The testability of this project is rather high. The main reason for this is that
the project is built strictly according to the MVC pattern. This has a few key
advantages when it comes to unit testing the application. First of all, a proper
MVC application is loosely coupled. By definition, the MVC pattern decouples the
application logic, display logic and persistence logic which is in sharp
contrast to regular page rendering systems (E.g., ASP.Net Web Forms).

We will discuss each important component and technique to show that there is
indeed high testability in this particular application.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Ninject
\subsection{Ninject}
Ninject is a dependency injection framework for .Net. Using dependency injection
it is possible to decouple the controllers from the actual data layer
implementation. In Listing~\ref{lst:lst1} a small snippet shows how the
\texttt{SnippetController} class is decoupled from actual implementation details
of the repositories. In the context of testing this enables us to mock up a test
repository with, for example, hardcoded values. Unit tests will not be aware of
this and thus totally oblivious of the fact that it is working with fake data.


\begin{lstlisting}[caption={Example of decoupling controller from data layer}, label={lst:lst1}]
public class SnippetController : Controller
{
    private ISnippetRepository snipRepo;
    private ILanguageRepository langRepo;
    private IUserRepository userRepo;
    private IGroupRepository groupRepo;

    ...
}
\end{lstlisting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Moq
\subsection{Moq}
As mentioned before, we use ``mocking'' implementations of data repositories to
unit test controllers. This is all well enough for small tests. However, this
approach does not scale properly. If you were to test the number of invocations
of a certain controller method one would simply add a field in the
\texttt{FakeRepository.cs} class and increment it each time the fake method is
called. This approach is problematic if the fake repositories grow too large to
maintain. One might even say that it would need unit testing. To mitigate this,
the \texttt{Moq} library was created. Moq allows one to easily
create fake repositories. An example of creating a fake repository is given in
Listing ~\ref{lst:moq}.

In this example we ask Moq to give us a class that implements the
\texttt{ISnippetRepository} interface. Moq then generates this class on the
fly. To specify behaviour for each method we can use some LINQ magic. The last
line in the example specifies that the method \texttt{m.GetSnippets()} should
simply return the array of \texttt{Snippet}s.

This way, we can easily generate test repositories. It is fairly obvious that
this approach is much less error prone that manually writing all the test
repositories.

\begin{lstlisting}[caption={Creating a mocking repository using Moq.}, label={lst:moq}]
Mock<ISnippetRepository> mock = new Mock<ISnippetRepository>();

Snippet[] snippets = new Snippet[] 
	{
	new Snippet() { Name = ``SSL Decryption'', ``User''=''cdetroye'',..},
	new Snippet() { Name = ``Windows Backdoor'', ``User''=''mvdcamme'',..},
	new Snippet() { Name = ``GPG Bruteforce algo'', ``User''=''cdetroye'',..},
	new Snippet() { Name = ``iCloud Hack'', ``User''=''mvdcamme'',..}
	};

mock.Setup(m => m.GetSnippets()).Returns(snippets);
\end{lstlisting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Controllers
\subsection{Controllers}
The key component of an MVC application is the controller. In this case testing
it is straightforward. Testing a controller is as simple as mocking up the above
mentioned repository for data. The unit test can then test if the returned model
is correct by means of testing the data that it contains. This does mean that we
can not test the actual representation. But this is rather an up- than
downside. An example of how to test a controller is given in
Listing~\ref{lst:testcontroller}. Note that it assumes the code of
Listing~\ref{lst:lst1} and ~\ref{lst:moq}.

\begin{lstlisting}[caption={Testing the model of a controller using Moq and Ninject.}, label={lst:testcontroller}]
  SnippetController c = new SnippetController(mock.Object);
  IEnumberable<Snippet> result = (IEnumberable<Snippet>)c.List(2).Model;

  // Assertions
  Snippet[] ss = result.ToArray();
  Assert.IsTrue(ss.Length == 4);
  Assert.AreEqual(ss[0].User, ``cdetroye'');
  Assert.AreEqual(ss[1].Name, ``Windows Backdoor'');
\end{lstlisting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Controllers
\subsection{Models}
Unit testing a model is rather trivial. In a strict MVC application these
classes do not contain any logic but merely carry data. Thus, unit
testing them would be as simple as writing some tests for a getter and a setter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Controllers
\subsection{Repositories}
Testing the repositories is also fairly straightforward. To do this we should
test the logic of the actual repositories. This can only be verified by actually
running data insertions, deletions and retrievals. Again, these tests should
prove to fairly straightforward. However, that might depend on the complexity of
the actual persistency layer. In our case this is entity framework that is
hooked up to a plain old SQL Server instance. This means that we keep raw SQL
queries at a distance and just program against the Entity Framework model. Thus,
relying on Entity Framework we can assume that testing beyond the interface of
Entity Framework is not required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Controllers
\subsection{HTML}
The final component of our application is the actual view. To test this we have
te resort to technology such as Selenium. Selenium is a framework that is built
for testing HTML user interfaces. Again, we can test each page seperatly.

\subsection{Conclusion}
We can conclude that by using all the frameworks and tools at hand it should be
possible to have the highest possible test coverage. We have the MVC pattern to
thank for this, as well as the top notch libraries like Moq and Ninject.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Test Strategy
\section{Test Strategy}

\subsection{Overall Test Strategy}
We plan on employing a wide array of different testing strategies, to maximize
the quality of our delivered software, in accordance with the principles of
agile programming. Testing will not happen ad-hoc, but will be structured and
integrated directly into the core of our development process.  In order to
maximize the number of tests that can take place, we will mainly focus on
creating tests that can be run and verified automatically, i.e., unit-tests.
However, we will also dedicate ourselves in part to manually explore our
application, to validate the overall quality of our software. This extends not
only to finding and solving any bugs that may be present, but also to making
sure that the runtime performance of our application is sufficiently high to
remain responsive.

Since it is in practice impossible to deliver an application completely free of
any errors, we will have to divide our time and choose which aspects of our
software will receive the most focus. We have therefore decided that the time
spent on a feature directly corresponds with the priority level of that feature:
high-priority features will receive the most attention, low-priority features
the least.

Concretely, we plan on using the following testing strategies.

\subsubsection*{Unit Testing}
Unit-tests will form the backbone of our testing strategy. Each developper will
create unit-tests simultaneously with implementing the various features.  If the
developper has finished writing the unit-test, the test will be run. If an error
is reported, the error should be fixed immediately.  Additionally, all
unit-tests that have been created will be run overnight and any errors should be
solved the following day.

\subsubsection*{Feature Testing}
In each iteration of our development process, we will release a number of new
features in our application. Once a feature has been completed, we will perform
manual testing on this feature to make sure it lives up to the expected
standards with regards to errors and runtime performance.
Since we are developping a web-application, we will rely on the Selenium
framework to automate our feature tests as
much as possible.

\subsubsection*{System Testing}
At the end of each iteration, we will execute manual, system-wide tests. These
tests will mostly be focused on verifying and validating the newly implemented
features, but they will also cover the existing features, in order to make sure
that the whole application lives up to the standards we have set for it.  While
testing these existing features, we will especially focus on the high-priority
features.

\subsubsection*{Integration Testing}
After completing or updating a module in our software, we will create automatic
integration tests to verify whether this module correctly interacts with the
other, already existing modules. Specific attention will be payed for
mission-critical modules, or modules specifically created to implement
high-priority features.

\subsection{Test Coverage}
Below, we describe how we will maximize the test coverage for each of our user
stories. We give an overview of the various tests we aim to create for these
stories.  Note that this set is only the minimum set of tests we will
complete. It is likely that, as we progress, we will uncover additional
opportunities for testing.

We start by examining the highest-priority features and progressively move on to
the lower-priority features.

\subsubsection*{Log in}
The most important step to be tested in the 'Log in' user story is the
validation of the log-in details, i.e., the e-mail address and the password.  It
should be possible to fully automate these kinds of tests, by storing dummy
user-data in the database and checking whether the validation process succeeds
when entering the correct details, and fails when entering incorrect data.  The
other steps in this user story can be verified with the Selenium framework.

\subsubsection*{Register}
The most important task here is again the validation process. This time however,
validation is more complex, since the application needs to make sure that no
user with the given e-mail address has already been registered, that the
password is strong enough and that the string that is provided as the given
e-mail address can indeed be parsed as an e-mail address, for example by making
use of a regular expressions matcher.  All of these tasks can be fully
automated, again by providing dummy data to the database. For the last task, we
should analyze the regexp that will be used and determine where the corner cases
of the expression lie.

\subsubsection*{Log out}
For this user-story, we will rely almost exclusively on the Selenium framework.

\subsubsection*{Create new snippet}
For this story, we will focus mainly on the step where the user-input, i.e., the
actual snippet along with all meta-data such as its name and id, are saved to
the database.  To this end, we will automatically generate snippets, store them
in the database and retrieve them immediately afterwards. If all data can be
retrieved, the test has succeeded.

\subsubsection*{Show snippet}
As with the other user stories, we will heavily rely on the Selenium framework
to test the input/output actions. However, when viewing a snippet, we should
make sure that syntax highlighting is correctly applied on the code that is
shown.  Because this syntax highlighting depends on the input language that was
chosen, as well as the code that was entered, testing the correctness of this
step will be an arduous task.  At the moment, we do not know of any technique
which would allow us to automatically verify whether syntax highlighting has
been correctly applied given a specific input program and programming language.
We will therefore have to rely on manual testing for this feature.

Testing this user story would go well hand-in-hand with the 'Create new snippet'
story: we could test the creation of one snippet and immediately afterwards
check whether this snipper is correctly displayed.  However, we do not wish to
completely rely on this technique, since we would then have to wait until both
features are fully implemented before we can start testing them. Furthermore, if
one feature were to fail, we would have delay testing the other feature until
the issue was fixed.

\subsubsection*{Edit user profile}
Testing for this user story will be similar to the testing of the 'Register'
story. We will again automatically generate mock data, use it to edit user
profiles that also have been automatically generated, and check whether the
correct changes have been made in the database.

\subsubsection*{Delete snippet}
It should be fairly straighforward to test this user story. We will again
automatically generate snippets and store them in the database. Afterwards, we
delete them and verify whether they have indeed been correctly removed.

\subsubsection*{Edit snippet}
Testing that a snippet can be edited should be similar to testing whether a user profile can be edited, although the data to be generated and the records to be changed are different of course.

\subsubsection*{Add profile picture}
This user story should again be fairly straightforward to test. The most important part to test would again be the actual saving of the profile picture to the disk.
Testing this can be accomplished by trying to upload a picture, checking whether the file-path to this picture has been correctly stored into the database, and corresponding the file at the file path with the image that was uploaded.
The two files could be compared based on their meta-data.
The various other steps of this story can again be tested through Selenium.

\subsubsection*{Create new group}
For this user story, the most important part to test is the saving of the details
of the new group. This can be done in a similar matter as the other features
where data is automatically generated, stored into and then retrieved from the
database.  The other aspects of this feature can be tested by using the Selenium
framework.

\subsubsection*{Show groups for user}
Since this feature should consist of no more than a simple database fetch,
followed by showing the retrieved data, which can be tested through the Selenium
framework, it should be trivial to create automatic tests for this feature.

\subsubsection*{Invite user}
As with the previous story map, it should be fairly straightforward to write
automatic tests for this feature, since it mainly consists of reading input and
showing output, for which we can use the Selenium framework.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Planning
\newpage
\section{Planning}
\subsection{Overall Planning}
\paragraph{Time Allocation}
For this project we have quite a lot of time with respect to
deadlines. Therefore we agreed to use each monday as a full
day to work on the project. A full day in this case equals 8 work hours. This
allows us to spend quite a lot of time on it in collaboration, which should decrease our communication overhead.

\paragraph{Slices}
We have 3 slices for this project: high, medium and low risk. Intuitively we can
consider the first slice as the most work. The reasoning behind this is that
there is alot of setup work to be done, getting to know the frameworks (i.e.,
Moq and Ninject) and general agreements to be made. Additionally, the first slice consists of the high-risk user stories, which require the most testing. Therefore we think it is a
good idea to give a generic ratio to each slice as an indication of how much
time they will take up. In Table~\ref{tbl:ratios} we show the ratios that we
find a good indication of the workload for each release. Given that the final
deadline for the project is probably around June, we took the first of June as
the final deadline. The time between our release dates was assigned in function of the time ratios the releases require and the total amount of time available. A quick calculation shows that that we have a total of 13
weeks available.
\begin{table}[h]
  \centering
  \label{tbl:ratios}
  \caption{Ratio of time per release}
  \begin{tabular}{| l| c| c| r | }
    \hline
    Release   & Time Ratio & Days of Work & Release Date \\
    \hline
    Release 1 & 60         & 7            & 20/04/2015 \\         
    Release 2 & 20         & 3            & 12/05/2015 \\
    Release 3 & 20         & 3            & 1/06/2015 \\
    \hline
  \end{tabular}
\end{table}

\subsection{Work per Release}
\paragraph{First} In the first release of the project we are planning to deliver the minimal
working project. This will contain the basic required functionality. This
contains being able to login and register to the site, create code snippets and
list personal snippets. We feel that other features are not as pressed to use this application.

\paragraph{Second} The second release will complete the features surrounding
snippets. A user should be able to delete snippets and edit them as well. The
reason we feel this is not high risk is that a user will probably want to use
this site in a pastebin-like manner, i.e., paste it, share it and be done with
it. In this release, we will also add a feature for editing user profiles.

\paragraph{Third} The third and final release will introduce the notion of
groups. This is the least important aspect of the entire application in our
opinion. The notion of groups only adds to the comfort of the user, but removing this feature would not make this application any less usable. As a final feature to be introduced, we will allow users to upload profile pictures.


% \begin{tabular}
%   Release 1 & 60 \\
%   Release 2 & 20 \\
%   Release 3 & 20 \\
% \end{tabular}


%$\mathsf{({m}^{3}/s)}$
%-------------------------------
%\begin{figure}
%   \setcapindent{-1em}
%    \fbox{\parbox{.95\linewidth}{
%	\centering\KOMAScript}}
%   \caption{Beispiel mit teilweise hängendem Einzug ab der zweiten Zeile}
%\end{figure}

%Guten Morgen\footnote{irgend ein text\label{refnote}}\multiplefootnoteseparator\footnote{es geht noch weiter}Blabla\footref{refnote}
\end{document}
